{\color{red}\textbf{TODO}}

### 2024-12-16 Paper draft/draft.tex
Updated version

Given $X^i$ matrices $i \in \left\{1, \dots, l \right\}$, we can rewrite the triggering conditions for each layer as:
\begin{equation}\label{eqn:etm-trigger}
  \widehat{\omega}^{i}(k) = \begin{cases}
    \phi^i(\nu^i(k)) & \text{if } {\xi^i}\tr X^i \xi > \rho^i \eta^i(k)\\
    \widehat{\omega}^{i}(k-1) & \text{otherwise}
  \end{cases}
\end{equation}
\begin{remark}\label{rem:eta-positive} \emph{Similarly to \citep[Lemma 3]{data-driven}, it can be demonstrated that $\eta^i$, the dynamic threshold of layer $i$, is always non-negative for any $\rho^i \in [0, 1)$, with the initial condition $\eta^i_0 \geq 0$.} \end{remark}
With respect to \eqref{eqn:etm-trigger} and \eqref{eqn:eta_dynamics} we have two possible occurrences:
\begin{itemize}
    \item $\widehat{{\xi^i}}\tr X^i \widehat{\xi^i} \leq \rho^i \eta^i$: It is trivial to verify that ${\eta^i}^+ = \rho^i \eta^i - \widehat{{\xi^i}}\tr X^i \widehat{\xi^i} \geq 0 $
    \item $\widehat{\xi^i}\tr X^i \widehat{\xi^i} > \rho^i \eta^i$: In this case, an event is triggered, and the vector $\widehat{\xi^i}$ gets updated to $\xi^i$ after the activation function application. In this situation, \eqref{eqn:sec_cond} is satisfied, and, with respect to Remark \ref{rem:sec-cond} and Lemma \ref{lem:finsler}, we have ${\xi^i}^\top X^i \xi^i < {\xi^i}^\top \Omega^i \xi^i < 0$. Once again, we have ${\eta^i}^+ = \rho^i \eta^i - {\xi^i}^\top X^i \xi^i > 0$.
\end{itemize}
By denoting 
\begin{equation}
    \bX = \text{diag} \pmx{R_1\tr X^1 R_1 & \dots & R_l\tr X^l & R_l}, \qquad \xi = \bmx{\tilde{x} \\ \tilde{\psi} \\ \tilde{\nu}}
\end{equation}
\begin{equation}\label{eqn:final-psi}
    \mathbf{\Psi_x} = \pmx{\Id_l \otimes \xi}\tr\! \bX \pmx{\1_l \otimes \xi}
\end{equation}
The ETM triggering condition and the dynamics of the dynamic thresholds can be rewritten in an element-wise fashion as:
\begin{equation}
\begin{aligned}
    \boldsymbol{\eta}^+ &= \bR \boldsymbol{\eta} - \mathbf{\Psi_x}\\
    \mathbf{\Psi_x} &> \bR \boldsymbol{\eta}\end{aligned}
\end{equation}

@@

We will first introduce a more compact notation for the system dynamics, along with some auxiliary matrices:
\begin{equation}\label{eqn:auxiliary}
\begin{aligned}
    \bar{A} &= A + B R_{\omega}\\
    \bar{B} &= -B N_{u \omega} R\\
    \tilde{x}^+ &= \bar{A}\tilde{x} + \bar{B}\tilde{\psi} + C \tilde{\Phi}\\
R_{\nu} &= \bmx{
  \Id & 0 & 0 \\
  0 & \Id & 0 \\
  R N_{\nu x} & \Id - R & 0\\
} \in \RR^{(n_x + n_{\phi} + n_q) \times (n_x + 2 n_{\phi})}\\
R_s &\in \RR^{(n_x + n_{\phi} + n_q) \times (n_x + n_q)}
\end{aligned}
\end{equation}

@@

\begin{proof}
By exploiting the inequality $$\bmx{\alpha (\widehat{\nu}^i_j)^{-2} - T^i_{j, j}}(\widehat{\nu}^i_j)^2\bmx{\alpha (\widehat{\nu}^i_j)^{-2} - T^i_{j, j}} \geq 0$$ having $(T^i_{j,j})^2(\widehat{\nu}^i_j)^2 \geq 2 \alpha T^i_{j,j} - \alpha^2 (\widehat{\nu}_j^i)^{-2}$, and assuming \eqref{eqn:inclusion}, we state:
$$
\bmx{
P & (T^i_{j,j} G^i_j)\tr\\
\star & (T^i_{j,j})^2(\widehat{\nu}^i_j)^2
} \geq 
\bmx{
P & {Z_j^i}\tr\\
\star & 2 \alpha T^i_{j,j} - \alpha^2 (\widehat{\nu}_j^i)^{-2}
} \geq 0
$$
That implies
$$
\bmx{
P & 0 & (T^i_{j,j} G^i_j)\tr\\
0 & 2 \Id & 0\\
\star & 0 &(T^i_{j,j})^2(\widehat{\nu}^i_j)^2
} \succeq 0
$$
We initially assume the positivity of $\boldsymbol{\eta}$, by pre- and post-multiplying for $\bmx{\tilde{x}\tr, \sqrt{\boldsymbol{\eta}}, 1}\tr$ and its transpose, and applying Schur's complement, we obtain
$$
\bmx{\tilde{x}\\ \sqrt{\boldsymbol{\eta}}}\tr \bmx{P & 0\\ 0 & 2 \Id} \bmx{\tilde{x}\\ \sqrt{\boldsymbol{\eta}}} \succeq \tilde{x}\tr \frac{(G^i_j)\tr (G^i_j)}{\widehat{\nu^i_j}^2} \tilde{x}
$$
This ensures $\cE(P, x_*) \subseteq S$, as defined in Remark \ref{rem:sec-set}. Now, assuming \eqref{eqn:finsler_constraint} holds for all $(x, \boldsymbol{\eta}) \in \cE(P, x_*)$, the application of Lemma \ref{lem:finsler} guarantees that $\boldsymbol{\eta} > 0$ as discussed in Remark \ref{rem:eta-positive}. Considering \eqref{eqn:nonlin-inclusion-constraint}, we have:
$$
\bmx{P & 0 & E_i\tr \\
0 & 2 \Id & 0 \\
E_i & 0 & \widehat{\mu_i}^2} \succeq 0
$$
By expressing $v_i = E_i x$ and pre- and post-multiplying by $\bmx{\tilde{x}\tr & \tilde{\Phi}(Ex)\tr}\tr$ we have:
$$
\bmx{\tilde{x}\\ \sqrt{\boldsymbol{\eta}}}\tr \bmx{P & 0\\ 0 & 2 \Id} \bmx{\tilde{x}\\ \sqrt{\boldsymbol{\eta}}} \succeq \tilde{x}\tr \frac{E_i\tr E_i}{\widehat{\mu_i}^2} \tilde{x} = \frac{v_i\tr v_i}{\widehat{\mu_i}^2} \succeq 0
$$
Once again, this ensures $\cE(P, x_*) \subseteq \bar{S}$ as defined in Assumption \ref{ass:nonlin}, and thus $\cE(P, x_*) \subseteq \left\{ S \cap \bar{S} \right\}$.

@@

The following plots refer to $\cS 4$ with $$
x_0 = \pmx{-9.43(deg) & 5.77(rad/s) &  0.0}\tr; \quad \boldsymbol{\eta}_0 = 0.01 \cdot \1$$ 
as initial configuration.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.45\textwidth]{Figures/ellipsoid_plot}
    \caption{Trajectory of the system within $\cE(P, x_*)$}
    \label{fig:ellipsoid}
\end{figure}

>>>>

Given $X^i$ matrices $i \in \left\{1, \dots, l \right\}$, we can rewrite the triggering conditions for each layer as:
\begin{equation}\label{eqn:etm-trigger}
  \widehat{\omega}^{i}(k) = \begin{cases}
    \phi^i(\nu^i(k)) & \text{if } {\xi^i}\tr X^i \xi > \rho^i \eta^i(k)\\
    \widehat{\omega}^{i}(k-1) & \text{otherwise}
  \end{cases}
\end{equation}
\begin{remark}\label{rem:eta-positive} \emph{Similarly to \citep[Lemma 3]{data-driven}, it can be demonstrated that $\eta^i$, the dynamic threshold of layer $i$, is always non-negative for any $\rho^i \in [0, 1)$, with the initial condition $\eta^i_0 \geq 0$.} \end{remark}
With respect to \eqref{eqn:etm-trigger} and \eqref{eqn:eta_dynamics} we have two possible occurrences:
\begin{itemize}
    \item $\widehat{{\xi^i}}\tr X^i \widehat{\xi^i} \leq \rho^i \eta^i$: It is trivial to verify that ${\eta^i}^+ = \rho^i \eta^i - \widehat{{\xi^i}}\tr X^i \widehat{\xi^i} \geq 0 $
    \item $\widehat{\xi^i}\tr X^i \widehat{\xi^i} > \rho^i \eta^i$: In this case, an event is triggered, and the vector $\widehat{\xi^i}$ gets updated to $\xi^i$ after the activation function application. In this situation, \eqref{eqn:sec_cond} is satisfied, and, with respect to Remark \ref{rem:sec-cond} and Lemma \ref{lem:finsler}, we have ${\xi^i}^\top X^i \xi^i < {\xi^i}^\top \Omega^i \xi^i < 0$. Once again, we have ${\eta^i}^+ = \rho^i \eta^i - {\xi^i}^\top X^i \xi^i > 0$.
\end{itemize}
By denoting 
\begin{equation}
    \bX = \text{diag} \pmx{{R^1}\tr X^1 R^1 & \dots & {R^l}\tr X^l & R^l}, \qquad \xi = \bmx{\tilde{x} \\ \tilde{\psi} \\ \tilde{\nu}}
\end{equation}
\begin{equation}\label{eqn:final-psi}
    \mathbf{\Psi_x} = \pmx{\Id_l \otimes \xi}\tr\! \bX \pmx{\1_l \otimes \xi}
\end{equation}
The ETM triggering condition and the dynamics of the dynamic thresholds can be rewritten in an element-wise fashion as:
\begin{equation}
\begin{aligned}
    \boldsymbol{\eta}^+ &= \bR \boldsymbol{\eta} - \mathbf{\Psi_x}\\
    \mathbf{\Psi_x} &> \bR \boldsymbol{\eta}\end{aligned}
\end{equation}

@@

We will first introduce a more compact notation for the system dynamics, along with some auxiliary matrices:
\begin{equation}\label{eqn:auxiliary}
\begin{aligned}
    &\bar{A} = A + B R_{\omega}\\
    &\bar{B} = -B N_{u \omega} R\\
    &\tilde{x}^+ = \bar{A}\tilde{x} + \bar{B}\tilde{\psi} + C \tilde{\Phi}\\
&R_{\nu} = \bmx{
  \Id & 0 & 0 \\
  0 & \Id & 0 \\
  R N_{\nu x} & \Id - R & 0\\
} \in \RR^{(n_x + n_{\phi} + n_q) \times (n_x + 2 n_{\phi})}\\
&R_s \in \RR^{(n_x + n_{\phi} + n_q) \times (n_x + n_q)}
\end{aligned}
\end{equation}

@@

\begin{proof}
By exploiting the inequality $$\bmx{\alpha (\widehat{\nu}^i_j)^{-2} - T^i_{j, j}}(\widehat{\nu}^i_j)^2\bmx{\alpha (\widehat{\nu}^i_j)^{-2} - T^i_{j, j}} \geq 0$$ having $(T^i_{j,j})^2(\widehat{\nu}^i_j)^2 \geq 2 \alpha T^i_{j,j} - \alpha^2 (\widehat{\nu}_j^i)^{-2}$, and assuming \eqref{eqn:inclusion}, we state:
$$
\bmx{
P & (T^i_{j,j} G^i_j)\tr\\
\star & (T^i_{j,j})^2(\widehat{\nu}^i_j)^2
} \succeq 
\bmx{
P & {Z_j^i}\tr\\
\star & 2 \alpha T^i_{j,j} - \alpha^2 (\widehat{\nu}_j^i)^{-2}
} \succeq 0
$$
That implies
$$
\bmx{
P & 0 & (T^i_{j,j} G^i_j)\tr\\
0 & 2 \Id & 0\\
\star & 0 &(T^i_{j,j})^2(\widehat{\nu}^i_j)^2
} \succeq 0
$$
We initially assume the positivity of $\boldsymbol{\eta}$, by pre- and post-multiplying for $\bmx{\tilde{x}\tr, \sqrt{\boldsymbol{\eta}}, 1}\tr$ and its transpose, and applying Schur's complement, we obtain
$$
\bmx{\tilde{x}\\ \sqrt{\boldsymbol{\eta}}}\tr \bmx{P & 0\\ 0 & 2 \Id} \bmx{\tilde{x}\\ \sqrt{\boldsymbol{\eta}}} \succeq \tilde{x}\tr \frac{(G^i_j)\tr (G^i_j)}{\widehat{\nu^i_j}^2} \tilde{x}
$$
This ensures $\cE(P, x_*) \subseteq S$, as defined in Remark \ref{rem:sec-set}. Now, assuming \eqref{eqn:finsler_constraint} holds for all $(x, \boldsymbol{\eta}) \in \cE(P, x_*)$, the application of Lemma \ref{lem:finsler} guarantees that $\boldsymbol{\eta} > 0$ as discussed in Remark \ref{rem:eta-positive}. Considering \eqref{eqn:nonlin-inclusion-constraint}, we have:
$$
\bmx{P & 0 & E_i\tr \\
0 & 2 \Id & 0 \\
E_i & 0 & \widehat{\mu_i}^2} \succeq 0
$$
By expressing $v_i = E_i x$ and pre- and post-multiplying by $\bmx{\tilde{x}\tr & \tilde{\Phi}(Ex)\tr}\tr$ we have:
$$
\bmx{\tilde{x}\\ \sqrt{\boldsymbol{\eta}}}\tr \bmx{P & 0\\ 0 & 2 \Id} \bmx{\tilde{x}\\ \sqrt{\boldsymbol{\eta}}} \succeq \tilde{x}\tr \frac{E_i\tr E_i}{\widehat{\mu_i}^2} \tilde{x} = \frac{v_i\tr v_i}{\widehat{\mu_i}^2} \succeq 0
$$
Once again, this ensures $\cE(P, x_*) \subseteq \bar{S}$ as defined in Assumption \ref{ass:nonlin}, and thus $\cE(P, x_*) \subseteq \left\{ S \cap \bar{S} \right\}$.

@@

The following plots refer to $\cS 4$ with $$
x_0 = \bmx{-9.43(deg) \\ 5.77(rad/s) \\  0.0}; \quad \boldsymbol{\eta}_0 = 0.01 \cdot \1; \quad d = 2.76(deg)$$ 
as initial configuration.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.45\textwidth]{Figures/ellipsoid_plot}
    \caption{Trajectory of the system within $\cE(P, x_*)$ and with respect to its projections}
    \label{fig:ellipsoid}
\end{figure}
